%-------------------------
% Resume in Latex
% Author : Taylor Kunke
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[backend=bibtex]{biblatex}

\addbibresource{BibTex_tkunke.bib}

\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-7pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}


\renewcommand{\labelitemii}{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://linkedin.com/in/tkunke/}{\huge Taylor Kunke}} & Email : \href{mailto:tkunke@gmail.com}{tkunke@gmail.com}\\
  \href{https://linkedin.com/in/tkunke/}{https://linkedin.com/in/tkunke/} & Mobile : \href{tel:(541) 760-1364}{(541) 760-1364} \\
\end{tabular*}

%-----------EXPERIENCE----------------

\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {NuScale Power}{Corvallis, Oregon}
      {Mechanical Engineer II/III}{July 2020 - Present}
      \resumeItemListStart
        	\item{Designed and procured a 1:10 scale model of a novel microreactor concept designed to utilize liquid metal working fluid with sodium-cooled heat pipes. Supported manufacturing efforts to ensure a high quality product for use in investor presentations.}
	\item{Led comprehensive, preliminary design review of the NuScale Power Module which incorporated multi-disciplinary assessment of design readiness and missing scope identification}
	\item{Redesigned the decay heat removal condenser to mitigate fabricability, inspection, and analysis/qualfication concerns.}
	\item{Performed initial ANSYS modeling and analysis of redesigned decay heat removal condenser for deadweight, seismic, and thermal loadings.}
        	\item{Prepared ASME BPVC Section III design specification for decay heat removal condenser and assisted with review of the NuScale Pipe Rupture Hazards Analysis report.}
	\item{Spearheaded engineering involvement with NX CAD modeling to invoke ownership of designs. Organized training and developed NXCustom configuration to interface with PLM integration tool.}
        	\item{Collaborated with multi-disciplinary subject matter experts to develop BOM-centric configuration control strategy focused on efficiency, ease-of-use, and productivity}
	\item{Performed ASME Section III piping analysis for Class 3 piping systems. Iterated design drawings and external inputs to the calculations to demonstrate design acceptability per code rules.}
	\item{Supported the licensing organization with incorporation of equipment specifications and design details into NuScale SDA, which resulted in an on-time and on-budget submittal to the Nuclear Regulatory Commission.}
      \resumeItemListEnd
\resumeSubSubheading
      {Summer Intern}{May - August, 2012, 2013, 2015}
      \resumeItemListStart
        	\item{Analyzed proprietary testing data to assess NuScale helical coil steam generator hydraulic performance.}
	\item{Developed an ANSYS substructure vibrational model of NuScale customized helical coil steam generator.}
	\item{Simulated ANSYS reactor building response to seismic excitation. Quantitatively analyzed various techniques to further improve seismic robustness against postulated earthquake loads.}
      \resumeItemListEnd
      
% --------Multiple Positions Heading------------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Space Exploration Technologies}{Hawthorne, California}
      {Test Automation Engineer I/II}{August 2017 - July 2020}
      \resumeItemListStart
        	\item{Responsible for the design, integration, and validation of multi-disciplinary component testing hardware for flight-like acceptance, development, and qualification testing programs.}
	\item{Designed and constructed high flow, thermally conditioned pressurized helium test facility for state-of-the-art rocket stage vent valves, enabling cost savings of over \$500,000 annually.}
	\item{Collaborated with external suppliers to procure high quality COTS solutions to ground support testing equipment.}
	\item{Investigated Dragon 2 in-flight abort static fire anomaly, leading a team of technicians towards the rapid diagnosis of system-related design flaw which guided efforts in system redesign.}
	\item{Analytically and experimentally evaluated heat transfer performance in heating and cooling applications, utilizing liquid nitrogen and thermal oil heat transfer fluids.}
	\item{Supported ground hardware teams with analysis and design of systems to meet strict flight requirements for testing while ensuring development programs could advance at the required pace.}
	\item{Designed and commissioned a fully-automated, 20 ksi pressure system to safely and efficiently test Raptor and Starship flight hardware with goal of Starship orbital flights in 2020.}
      \resumeItemListEnd

    \resumeSubheading
      {Georgia Institute of Technology - Sustainable Thermal Systems Lab}{Atlanta, Georgia}
{Graduate Research Assistant}{August 2015 - July 2017}

      \resumeItemListStart
        \item{Designed an air-coupled condenser wind tunnel test facility to study the impacts of dynamically unstable oscillating reeds on air-side heat transfer performance.}
        \item{Procured air-coupled condenser representative test section and generated testing procedures to evaluate heat transfer enhancement and pressure drop penalty associated with novel reed design.}
        \item{Wrote a bespoke heat transfer/pressure drop analysis code to assess overall power plant efficiency improvement. Incorporated empirical data from test facility into the code for the purposes of economic and environmental implications.}
      \resumeItemListEnd
\resumeSubSubheading
{Undergraduate Research Assistant}{May 2014 - August 2014}
      \resumeItemListStart
    	\item{Designed and constructed pin-fin heat exchanger test facility to study effects of pin geometry on pressure drop and mass transfer for implementation in absorption refrigeration systems.}
	\item{Investigated flow regime development in pin-fin geometry using high-speed visualization equipment and MATLAB video tools.}
	\item{Developed segmented air-cooled condenser coupled heat transfer, fluid mechanics, and thermodynamics design code in Engineering Equation Solver (EES).}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading
      {Georgia Institute of Technology}{Atlanta, Georgia}
      {Master of Science in Mechanical Engineering}{August 2015 -- July 2017}
      \resumeItemListStart
        \item{3.71 GPA. Presidential Fellowship recipient.}
      \resumeItemListEnd

   \resumeSubheading
      {Gonzaga University}{Spokane, Washington}
      {Bachelor of Science in Mechanical Engineering, Summa Cum Laude }{August 2011 -- May 2015}
      \resumeItemListStart
        \item{GPA: 3.93. President’s List recognition for eight semesters. Presidential Scholarship recipient. Tau Beta Pi member.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------CORE COMPETENCIES-----------------
\section{Core Competencies}
  \resumeSubHeadingListStart
    \resumeSubItem{Certifications}
      {EIT (Washington)}
    \resumeSubItem{Mechanical Design}
      {NX, SolidWorks, DesignModeler, SpaceClaim}
    \resumeSubItem{Mechanical Analysis}
      {ANSYS Workbench/Mechanical, AutoPIPE, EES}
    \resumeSubItem{Programming}
      {NXOpen, git, APDL, Python, Matlab, MathCAD, LabView}
    \resumeSubItem{Industrial Code Experience}
      {ASME BPVC, Section III (2017), ASME Y14.5 (2018), USAF TO 00-25-223 (2017)}
  \resumeSubHeadingListEnd

%-----------PUBLICATIONS-----------------
\vspace{0pt}
\section{Publications}

\nocite{*}
\DeclareFieldFormat{labelnumberwidth}{}
\setlength{\biblabelsep}{-0pt}
\printbibliography[heading=none]
\
%-------------------------------------------
\end{document}
